Efficiently stable presentations from error-correcting codes

### 2023-10-02 efficient_stability.tex
Updates from Overleaf

As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}. By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}. With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}. This turns up to be  tight:
\begin{claim}
    Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$. There is a $(\nicefrac{2}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism. Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
\end{claim}

@@

\begin{remark}
The infinity norm example. Ref to Appendix.    
\end{remark}

>>>>

As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on both the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}, and its \emph{Dehn function} --- namely, the minimal volume of a Van Kampen diagram with perimeters of length $3$. By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}. With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}. This turns up to be  tight:
\begin{claim}
    Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$. There is a $(\nicefrac{2}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism. Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
\end{claim}

@@

\begin{remark}
Henry's infinity norm example. Ref to Appendix.    
\end{remark}
